Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-25 paper/paper.tex
comment to discuss flooding

It is worth noting that we found empirically that deciding which
reverse engineering strategy to use based on the protocol was
effective. We used the payload strategy for http and the field
strategy for the other protocols. At the end of this step,
\tname\ produces a seed rule that captures the malicious traffic by
definition.

@@

\begin{figure*}[t!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-contents}Number of content options.}
\end{subfigure}% <---- don't forget this %
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-rule-size}Rule sizes.}
\end{subfigure}%
%\vspace{1ex}
\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-3ex}  
  \caption{\label{fig:distribution-strings}Strings used as parameters of content options.}
\end{subfigure}%
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{subfigure}%
\vspace{-1ex}
  \caption{Distribution of features.}
\end{figure*}

@@

    \midrule
    Ping Scan & 5 & - & - \\
    SYN Flood & 2 & - & - \\
    JBoss JMX & 23 & - & 23 \\
    WeBid & 23 & - & -\\    
    ColdFusion & 19 & - & 5\\
    .htaccess access & 17 & - & 2\\
    .idq access & 19 & - & 2 \\
    iisadmin access & 17 & - & 1 \\
    /system32/ in URI & 20 & - & 2 \\
    Script tag in URI & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

It is worth noting that we found empirically that deciding which
reverse engineering strategy to use based on the protocol was
effective. We used the payload strategy for http and the field
strategy for the other protocols.\Mar{discuss flood cases...} At the end of this step,
\tname\ produces a seed rule that captures the malicious traffic by
definition.

@@

\begin{figure*}[t!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-contents}Number of content options.}
\end{subfigure}% <---- don't forget this %
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-rule-size}Rule sizes.}
\end{subfigure}%
%\vspace{1ex}
\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-3ex}  
  \caption{\label{fig:distribution-strings}Strings used as parameters of content options.}
\end{subfigure}%
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{subfigure}%
\vspace{-1ex}
  \caption{Distribution of features.}
  \Luc{@Marcelo, estamos utilizando mais uma distribuicao agora. Precisamos adicionar o grafico dela tb?}
\end{figure*}

@@

    \midrule
    Ping Scan & 5 & 2 & - \\
    SYN Flood & 2 & 2 & - \\
    JBoss JMX & 23 & 381 & 23 \\
    WeBid & 23 & - & -\\    
    ColdFusion & 19 & 39 & 5\\
    .htaccess access & 17 & 2458 & 2\\
    .idq access & 19 & 1111 & 2 \\
    iisadmin access & 17 & 861 & 1 \\
    /system32/ in URI & 20 & 3665 & 2 \\
    Script tag in URI & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}
